A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility

### 2019-05-15 paper.Rmd
add reference to introduction; restructure heading levels for section 9 on the minimal structure for researchers

Data are a fundamental currency upon which scientific discoveries are made. Without access to good data, it becomes extremely difficult, if not impossible, to advance science. Yet, a large majority of data on which published research papers are based rarely see the light of day and are only visible to the original authors [@Rowhani-Farid2016; @Stodden2018].  Sharing data sets upon publication of a research paper has benefits to individual researchers, often through increased visibility of the work [@Kirk2019]. But there is also a component of benefit to the broader scientific community. This primarily comes in the form of potential for reuse in other contexts along use for training and teaching (@McKiernan2016). Assuming that the data have no privacy concerns (e.g., human subjects, locations of critically endangered species), or that the act of sharing doesn't put the authors at a competitive disadvantage, sharing data will always have a net positive benefit. First and foremost, sharing data along with other artifacts can make it easier for a reader to independently reproduce the results, thereby increasing transparency and trust in the work. The act of easy data sharing can also improves model training, as many different models can be tried and tested on latest data sources, closing the loop on research and application of statistical techniques. Existing data sets can be combined or linked with new or existing data, fostering the development and synthesis of new ideas and research areas. The biggest of these benefits is the overall increase in reproducibility.

@@

# README: A Human readable description of the data

@@

# Codebook: Human readable dictionary of data contents

@@

# License: How to use and share the data

@@

**CC BY**

@@

**CC0**

@@

# Citation: How you want your data to be cited

@@

# Machine readable metadata

@@

# Raw data: The original/first data provided

@@

# Scripts: To clean raw data ready for analysis

@@

# Analysis ready data: Final data used in analysis

@@

## Tooling for packaging data

NOTE: not sure if this quite fits here, tooling is important, but at the moment we are not sure if we should describe all tooling, as I will have a lot of examples for R, and not for Python/Julia

@@

### Dataset 1: Forest Census Plot on Barro Colorado Island

@@

### Dataset 2: Sensor data

@@

### Dataset 3: Most other datasets

>>>>

Data are a fundamental currency upon which scientific discoveries are made. Without access to good data, it becomes extremely difficult, if not impossible, to advance science. Yet, a large majority of data on which published research papers are based rarely see the light of day and are only visible to the original authors [@Rowhani-Farid2016; @Stodden2018].  Sharing data sets upon publication of a research paper has benefits to individual researchers, often through increased visibility of the work [Popkin2019; @Kirk2019]. But there is also a component of benefit to the broader scientific community. This primarily comes in the form of potential for reuse in other contexts along use for training and teaching (@McKiernan2016). Assuming that the data have no privacy concerns (e.g., human subjects, locations of critically endangered species), or that the act of sharing doesn't put the authors at a competitive disadvantage, sharing data will always have a net positive benefit. First and foremost, sharing data along with other artifacts can make it easier for a reader to independently reproduce the results, thereby increasing transparency and trust in the work. The act of easy data sharing can also improves model training, as many different models can be tried and tested on latest data sources, closing the loop on research and application of statistical techniques. Existing data sets can be combined or linked with new or existing data, fostering the development and synthesis of new ideas and research areas. The biggest of these benefits is the overall increase in reproducibility.

@@

## README: A Human readable description of the data

@@

## Codebook: Human readable dictionary of data contents

@@

## License: How to use and share the data

@@

### CC BY

@@

### CC0

@@

## Citation: How you want your data to be cited

@@

## Machine readable metadata

@@

## Raw data: The original/first data provided

@@

## Scripts: To clean raw data ready for analysis

@@

## Analysis ready data: Final data used in analysis

@@

# Tooling for packaging data

<!-- NOTE: not sure if this quite fits here, tooling is important, but at the moment we are not sure if we should describe all tooling, as I will have a lot of examples for R, and not for Python/Julia -->

@@

## Dataset 1: Forest Census Plot on Barro Colorado Island

@@

## Dataset 2: Sensor data

@@

## Dataset 3: Most other datasets
